\Title

### 2022-09-13 Grimaldi-etal-BiolCybernetics.tex
task

%
%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{Abe}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.

>>>>

%
%\ninept
%
%\abstract{Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{abeles_role_1982}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.
